Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-04-07 Writing/appendix.rmd

The size of random yield error $\varepsilon$ should be coordinated with the potential yield level for a site $(i,j)$.  To do so, we first created spatially autocorrelated weights $r^{\varepsilon}_{i,j} \in (-1,1)$. After $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$ were generated, then $\varepsilon_{i,j}$ was determined by interacting $r^{\varepsilon}_{i,j}$ with the deterministic part of yield (i.e., $ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))$). This process can be expressed by rewriting Eq. \@ref(eq:eqn3) as follows. The observed yield at site $(i, j)$ (i.e., $y_{i,j}$) is:

@@

Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$<!--  $\varepsilon_{i,j}$ -->, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) <!-- The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$. See Figure C.1 for an example of the generated parameters.  -->

@@

The figure XX plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario. The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yields well.

@@

```{r vis-y-pred, fig.width=7, fig.height=7.5, fig.cap = "Figure E.1: True yields without error and predicted yields"}
vis_y_pred
```

@@

## Appendix G: Simulations with Different Size of Yield Disturbance Term.
In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$). We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study by changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$. Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($0.0225$) was used to create yield datasets with high yield error. Figure G.1 illustrates examples of the generated low and high $\varepsilon$.

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An example of experimental design of N and generated yield at the subplot resolution", cache = TRUE}
field_m_error_low | field_m_error_high
```

@@

As the size of yield error increases, EONR estimation and yield prediction accuracy becomes improved. However, qualitative results about the comparative advantage of CF over other models remain the same, and Table G.3 consistently illustrates that good performance in yield prediction does not necessary indicate good performance in EONR estimation.

>>>>

The size of random yield error $\varepsilon$ needs to be coordinated with the potential yield level for a site $(i,j)$.  To do so, we first created spatially autocorrelated weights $r^{\varepsilon}_{i,j} \in (-1,1)$. After $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$ were generated, then $\varepsilon_{i,j}$ was determined by interacting $r^{\varepsilon}_{i,j}$ with the deterministic yield component (i.e., $ymax_{i,j}(1-exp(\alpha_{i,j} + \beta_{i,j} \cdot N_{i}))$). This process can be expressed by rewriting Eq. \@ref(eq:eqn3) as follows. The observed yield at site $(i, j)$ (i.e., $y_{i,j}$) is:

@@

Table C.1 shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $r^{\varepsilon}_{i,j}$<!--  $\varepsilon_{i,j}$ -->, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes], or as a Github repository at https://github.com/Shunkei3/VRA_with_CF.git.) See Figure C.1 for an example of the generated parameters.<!-- The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $\alpha$, $\beta$, $ymax$, and $\varepsilon$ were assumed to be $-0.5$, $0$, $12,000$ kg/ha, and $0$, and their sills were assumed to be $0.02$, $1.0$, $2.0 \times 10^{6}$ kg/ha, and $0.015$. See Figure C.1 for an example of the generated parameters.  -->

@@

Figure E.1 plots the predicted yields against the true yield without error in one of the one thousand simulation rounds by ML method and modeling scenario. The predicted points clustered around the red 1-to-1 line, meaning that the prediction-oriented ML methods predicted yields well.

@@

```{r vis-y-pred, fig.width=7, fig.height=5, fig.cap = "Figure E.1: True yields without error and predicted yields"}
vis_y_pred
```

@@

## Appendix G: Simulations with Different Size of Yield Disturbance Term.
In this section, we present the results of EONR estimation and yield prediction with different size of random yield error ($\varepsilon$). By changing the variogram parameter of $psill$ for $r^{\varepsilon}_{i,j}$, We created two additional yield datasets	that are only different in the size of $\varepsilon$ from the yield datasets we used in the study. Half size of $psill$ value ($0.0075$) was used to create yield datasets with low yield error, and one and a half size of $psill$ value ($0.0225$) was used to create yield datasets with high yield error. Figure G.1 illustrates examples of the generated low and high $\varepsilon$.

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "Figure G.1: An illustrative example of spatial distributions of different size of yield errors", cache = TRUE}
field_m_error_low | field_m_error_high
```

@@

As the size of yield error increases, EONR estimation and yield prediction accuracy becomes improved. However, qualitative results about the comparative advantage of CF over other models remain the same, and Table G.3 illustrates that good performance in yield prediction does not necessary indicate good performance in EONR estimation.
